---
title: "Predictors of Body Fat"
author: "by Sahir Bhatnagar"
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    theme: flatly
    highlight: tango
    fig_caption: yes
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true
bibliography: 001-bibliography.bib
link-citations: yes
---

```{r setup, include=FALSE}
# can set global options here
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# you can create custom chunk options
knitr::opts_template$set(
  fig.large = list(fig.width = 7, fig.height = 5, fig.align = 'center', fig.pos = 'h'),
  fig.small = list(fig.width = 6, fig.height = 4, fig.align = 'center', fig.pos = 'h'),
  fig.full = list(fig.width = 8, fig.height = 6, fig.align = 'center', fig.pos = 'h')
)


# paths for data and scripts location
data_path <- "~/git_repositories/CSSC2018/001-motivating-example/data/"
bin_path <- "~/git_repositories/CSSC2018/001-motivating-example/bin/"

# read in scripts. Note: this will not run the code. 
# Like a 'promise'
knitr::read_chunk(paste0(bin_path, "001-packages.R"))
knitr::read_chunk(paste0(bin_path, "001-data.R"))
knitr::read_chunk(paste0(bin_path, "001-analysis.R"))
```


```{r required-packages, echo = FALSE, results = 'hide'}
```


# Introduction

Identifying overweight populations is an important first step in fighting the obesity epidemic. However, accurate measure of body fat are costly and inconvenient. Therefore we are interested in determining predictors of body fat which require only a scale and a measuring tape. We analyze a dataset which contains percentage of body fat, age, weight, height and ten body circumference measurements for 251 men [@johnson1996fitting; @penrose1985generalized]. We model the data using multiple linear regression and perform various model selection techniques.

<br>


# Exploratory Analysis

```{r import-data}
```

A pairs plot is presented in Figure \@ref(fig:pairs)

```{r pairs, fig.cap='Pairs plot of Body Fat data', opts.label = 'fig.large'}
```

We will fit a linear regression model of the form

\begin{multline}
pbf1_i= \beta_0+\beta_1\textrm{age}_i+\beta_2\textrm{weight}_i+\beta_3\textrm{height}_i+\beta_4\textrm{neck}_i \\
+\beta_5\textrm{chest}+\beta_6\textrm{abdomen}_i+\beta_7\textrm{hip}_i+\beta_8\textrm{thigh}_i+\beta_9\textrm{knee}_i \\
+\beta_{10}\textrm{ankle}_i+ \beta_{11}\textrm{bicep}_i +\beta_{12}\textrm{forearm}_i +\beta_{13}\textrm{wrist}_i + \varepsilon
\end{multline}


# Results

The parameter estimates of the linear model and their standard errors are shown in the table below:

<br>

```{r fit1}
```

```{r fit1-coef, results = 'asis'}
```

<br>

Model diagnostics are shown in Figures \@ref(fig:diagnostics) and \@ref(fig:influence-plot)

```{r diagnostics, fig.asp = 0.7, fig.width = 6, fig.align = 'center', results='hide',fig.cap = c('Diagnostic 1','Diagnostic 2','Diagnostic 3','Diagnostic 4')}
```

<br>


```{r influence-plot, results = 'hide', opts.label = 'fig.small', fig.cap = 'Regression influence plot'}
```


<br>

Look more closely at observation 42:

```{r}
knitr::kable(DT[42,.(pbf1,weight,height),])
```

It's unlikely someone weighs 205 pounds and only has a height of 29.5 inches. 

<br>

# Sensitivity Analysis

We perform the same analysis as above, but with observation 42 removed

```{r fit2}
```


We compare both fits in the following table:

<br>


```{r compare-fits, results = 'asis'}
```




# References
